---
title: "Project_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Question 1:
Supervised learning is the machine learning task of learning a function that maps an input to an output based on example input-output pairs. Unsupervised learning is a type of algorithm that learns patterns from untagged data. For Supervised learning, for each observation of predictor measurements(s) xi, i = 1,...,n there is an associated response measurement yi. We wish to fit a model that relates the response to the predictors, with the aim of accurately predicting the response for future observartions or better understanding the relationship between the response and the predictors(page #26 of book). By contrast, unsupervised learning describes the somewhat more challenging situation in which for every observation i = 1, ...,n, we observe a vector of measurement xi, but no associated response yi (page #26 of book).Supervised learning methods such as Linear regresssion, Logistic regression, k-nearest(. However, unsupervised learning is not possible to fit linear regression model, since there is no response varaible to predict(page #26 of book.) 



Question 2:
According to Regression model, Y is quantitative, which is Numerical values, for example price, blood, and pressure. According to Classification model, Y is qualitative, which is categorical values for example survived/died, spam/not spam (Lecture 2). However, the distinction is not always that crisp(page #28 of book.). Least squares linear regression is used with a quantitative response, whereas logistic regression is typically used with a qualitative response. Thus, despite its name, logistic regression is a classification method(page #28 of book.). But since it estimates class probabilities, it can be taught of as a regression method as well(page #28 of book.)



3.
regression model = MSE, RMSE, MAE
classification model = Accuracy, Confusion Matrix



4.
Predictive : Aim is to predict Y with minimum reducible error, and not focused on hypothesis tests.

Descriptive : Choose model to best visually emphasize a trend in data, for example using a line on a scatterplot

Inferential : Aim is to test theories, and state relationship between outcome & predictor. 















install.packages("tidyverse")
install.packages("tidymodels")
install.packages("ISLR")
install.packages("ggplot2")

library(ggplot2)

#1
```{r}
ggplot(mpg, aes(x=hwy)) + geom_histogram()
```


#2
```{r}
ggplot(mpg, aes(x=hwy, y=cty)) + geom_point()

```


#3
```{r}
ggplot(mpg, aes(x = manufacturer)) + geom_bar() + coord_flip()
```







#4

install.packages("tidyverse")
library(tidyverse)

library(ggplot2)

data(mpg)

boxplot(hwy ~ cyl, data = mpg,col = c("green", "green", "green","green"))

ggplot(mpg, aes(group = cyl, y = hwy)) + geom_boxplot()


From the above output, the following are interpreted,

If the value of cyl is high, hwy value is decreased.
If the value of cyl is low, hwy value is increased.
The lowest and highest value of cyl is having outliers.



#5
install.packages("corrplot")
library(corrplot)
M <- cor(mpg)
head(mpg)
my_data <- filter(mpg, displ, cyl, cty, hwy)
M = cor(my_data)


head(round(M,2))

corrplot(M, type="lower")


